First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-10-19 MY_PUBLICATIONS/PRL/prl.tex
updated

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
  neutron recoil momenta from 0.460 GeV/c up to 1.14 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions have also been suppressed by choosing a kinematic region where the neutron recoil
  angle is between 35 and 45 degrees with respect to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment \cite{halla_deut_2011}
  and is also predicted in modern theoretical calculations \cite{sargsian_2015}. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and
  comparisons between measured and predicted cross sections become sensitive to the deuteron momentum distributions.

@@

>>>>

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at 4-momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
  neutron recoil momenta up to 1.18 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions (FSI) have also been suppressed by choosing a kinematic region where the neutron recoil
  angle ($\theta_{nq}$) is between 35 and 45 degrees with respect to the 3-momentum transfer, $\vec{q}$. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and comparison
  to recent theoretical calculations show data to be sensitive to momentum distributions up to $\sim$ 700 MeV/c recoil momenta.

@@

%--------------MOTIVATION / introduction (from my proposal)--------------
